\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
small modifs
notation change

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link from a neuron $i$ to a neuron $j$.
The network inference task is set as follows :
\textit{Given the observations $(x_t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
of graph $G$, where $\mathbb{1}$ is the indicator function.}

>>>>

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
The connectomes, the neural network, is represented by a (un)directed graph $G = (V, E)$ comprising
a set of nodes $V$ and a set of edges $E \subseteq \left\{(i, j) \in V \times
V\right\}$, (un)ordered pair from $V$.
Each node $i \in V$ represents a neuron, and each edge $(i, j) \in E$
represents a direct link from a neuron $i$ to a neuron $j$.
The network inference task is set as follows :
\textit{Given the observations $(x^t \in \mathcal{R}^{|V|})_{t=1}^T $
along $T$ periods of time of the $|V|$ neurons, the goal is to infer the
adjacency matrix $A : a_{i,j} = \mathbb{1}((i, j) \in E)$ of the neural network
of graph $G$, where $\mathbb{1}$ is the indicator function.}
